The SMT Competition 2015--2018

### 2019-04-15 2018/report/SMT-COMP.tex
Report: Remove frames
Report: Fix weighted division score

\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
The \emph{(weighted) score} of a solver in a division of the \maintrack and
\ucoretrack is then defined as the weighted sum of all raw scores $$\sum_{i\in
F} \alpha'_i \cdot \langle e \cdot N, n \cdot N, w, c\rangle$$ where the sum is
over all benchmarks in the division to assess parallel performance, and the
weighted sum of all sequential scores to assess sequential performance.

>>>>

\paragraph{Weighted Division Scores (\maintrack and \ucoretrack 2016-2018).}
The \emph{(weighted) score} of a solver in a division of the \maintrack and
\ucoretrack is then defined as the weighted sum of all raw scores $$\sum_{i\in
F} \alpha'_i \cdot \langle e_i \cdot N_i, n_i \cdot N_i, w_i, c_i\rangle$$
where the sum is over all benchmarks in the division to assess parallel
performance, and the weighted sum of all sequential scores to assess sequential
performance.
